### 2025-01-28 paper/icml25/first/sects/introduction.tex
add a sentence about inspiration of our work (@f14-bertolotti check)

In this work, we aim to address both limitations by approximating the gradients of the differentiable simulator. Specifically, we propose replacing both the simulator and the reward function with two neural networks trained alongside the policy and value networks. This approach is designed to create an algorithm that is more robust to complex dynamics and sparse rewards, enabling it to function effectively across a broader range of environments, including both single-agent and multi-agent scenarios. However, this method also introduces additional complexity and computational overhead due to the need for training these additional networks.

>>>>

In this work, we aim to address both limitations by approximating the gradients of the differentiable simulator inspired by model-based reinforcement learning algorithms~\cite{DBLP:conf/icml/HafnerLFVHLD19,DBLP:conf/iclr/HafnerLB020}.
Specifically, we propose replacing both the simulator and the reward function with two neural networks trained alongside the policy and value networks. This approach is designed to create an algorithm that is more robust to complex dynamics and sparse rewards, enabling it to function effectively across a broader range of environments, including both single-agent and multi-agent scenarios. However, this method also introduces additional complexity and computational overhead due to the need for training these additional networks.
